\documentclass[a4paper,9pt]{article}
\usepackage[top=0.7in, bottom=0.7in, left=0.7in, right=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{parskip}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage{url}  

\setlength{\columnsep}{20pt}
\setlength{\parskip}{0pt}
\titlespacing{\section}{0pt}{4pt}{2pt}
\titleformat{\section}{\bfseries\large\raggedright}{}{0em}{}

\newcommand{\resumesection}[1]{%
  \vspace{6pt}
  \section*{#1}
  \hrule\vspace{4pt}
}

\begin{document}


{\LARGE \textbf{Pericharla Sravanthi}} \\[-1pt]

\begin{tabularx}{\textwidth}{@{} l X @{\hspace{25pt}} l X @{\hspace{6pt}} l X @{}}
\textcolor{black}{\faEnvelope} & \href{mailto:sravanthipericharla23@gmail.com}{sravanthipericharla23@gmail.com} &
\textcolor{black}{\faPhone*}~ & \makebox[0pt][l]{8639831217} &
\textcolor{black}{\faLinkedin} & \href{https://linkedin.com/in/sravanthi23}{linkedin.com/in/sravanthi23} \\
\textcolor{black}{\faMapMarker*} & Kesanakurru &
\textcolor{black}{\faGithub}~ & \href{https://github.com/Sravanthi-Pericharla}{\texttt{github.com/Sravanthi-Pericharla}} &
&
\end{tabularx}
\resumesection{Career Objective}
Seeking a position to utilize my knowledge,
skills and abilities in the company that
offers a competitive environment, a true
profession put in the acquired knowledge
and gain exposure to upcoming
technologies while being resourceful,
innovative and flexible.

\resumesection{Education}
\textbf{B.Tech in CSE}, GMR Institute of Technology \\
CGPA: 9.42 (upto 5th semester) \hfill 2022 – 2026

\textbf{Intermediate (MPC)}, Sri Aditya Junior College, Kakinada \\
Percentage: 98.1\% \hfill 2020 – 2022

\resumesection{Experience}
\textbf{Cloud Computing Intern} — Hashtek Solutions \\
Vishakapatnam, July 2024
\begin{itemize}[leftmargin=*, noitemsep]
    \item Managed EC2 instances, VPC configurations, and static site hosting on Amazon S3.
    \item Set up PostgreSQL using RDS; implemented Auto Scaling, Load Balancer, and Bastion host for better reliability and security.
\end{itemize}

\resumesection{Projects}
\textbf{Suspicious Individual Detection in Public Spaces} \hfill

\href{https://github.com/Sravanthi-Pericharla/crowd_detection}{\texttt{[GitHub]}}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Designed a real-time surveillance system using YOLOv8 and DeepFace for individual recognition.
    \item Built a full-stack web app using ReactJS frontend and Flask backend with SQLite for storing logs and data.
    \item Integrated Twilio API to automatically alert authorities via SMS when criminals are detected in live video.
    \item Ensured security with hashed face encodings and implemented efficient matching algorithms to reduce false positives.
\end{itemize}

\resumesection{Skills}
\noindent\begin{minipage}{\textwidth}
\begin{multicols}{2}
\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Languages:} Python, Java, C
    \item \textbf{Web:} HTML, CSS
    \item \textbf{Tools:} SQLite
    \item \textbf{Domains:} ML, DL, Cloud (AWS)
    \item \textbf{CS Core:} DBMS, DSA, SQL
    \item \textbf{Soft Skills:} Leadership, Teamwork
\end{itemize}
\end{multicols}
\end{minipage}

\resumesection{Certificates}
\noindent\begin{minipage}{\textwidth}
\begin{multicols}{2}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Affective Computing – NPTEL
    \item Cloud Computing – Hashtek
    \item Data Analytics – EDX
    \item Multicloud Associate – Aviatrix
    \item Python Essentials – Cisco
    \item OOP in Java – Coursera
\end{itemize}
\end{multicols}
\end{minipage}

\resumesection{Achievements}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Awarded the FFE Amazon Scholarship thrice for consistent academic excellence.
    \item Completed the FFE Mentornship Program under guidance of a Microsoft professional, gaining real-world project exposure.
    \item Selected for the prestigious FLY-Scholar program by CMI, USA, focused on leadership and cognitive growth.
    \item Runner-up in Interdepartmental Badminton Tournament, GMRIT Annual Sports Day 2025.
    \item Successfully organized college-level tech events as CSI Coordinator with 100+ participants.
\end{itemize}

\resumesection{Positions of Responsibility}
\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Secretary, CSI Student Chapter}, GMRIT (2024–25): Coordinated monthly technical events, communicated with faculty, and led the planning of workshops, coding contests, and student inductions.
\end{itemize}


\resumesection{Participations}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Code Wars 2023 – Competitive coding contest at GMRIT.
    \item Datathon 2023 – Overnight analytics hackathon at GMRIT.
\end{itemize}

\end{document}
